Using traffic analysis to identify The Second Generation Onion Router

### 2011-06-12 ieee-conference-paper/paper.tex
Start work on results section

@@

@@

In fact, if i

@@

>>>>

% code listings
\RequirePackage{listings}
\lstset{
  basicstyle=\ttfamily,
  xleftmargin=36pt,
  xrightmargin=12pt,
  numberstyle=\tiny,              % the size of the fonts that are used for the line-numbers
  numbers=left,                   % where to put the line-numbers
  stepnumber=1,                   % the step between two line-numbers. If it's 1 each line
  tabsize=2,                      % sets default tabsize to 2 spaces
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=true,         % sets if automatic breaks should only happen at whitespace
  escapeinside={\%*}{*)},         % if you want to add a comment within your code
  showstringspaces=false,         % don't show spaces in strings as little _ style characters
}

@@

To determine if Tor traffic can be distinguished from regular encrypted
traffic, an experiment was conducted to generate a series of traces for
comparison. HTTPS traffic was generated using the commonly available Firefox
browser, with a series of typical user interactions simulated with the Selenium
browser testing framework. The same simulations were run through a simulated
Tor network using both the HTTP and HTTPS protocol.

@@

Investigating more closely, by examining individual packet traces some
significant patterns begin to appear. Table \ref{table:packet_sizes} shows the
packet sizes seen for the first 10 packets of a 1\% sample of sessions in each
phase of data captured. The first few packets contain 0 bytes of data, these
are the typical SYN, SYN/ACK and ACK flagged packets that are used to initiate
a TCP/IP connection. Following that only two packet sizes are seen for HTTP
connections 100 and 110. For Tor sessions a range of packet sizes from 131 to
152. This knowledge can be used to build a very rudimentary classification
algorithm to identify Tor traffic, as seen in the pseudo-code below:

@@

\begin{lstlisting}[language=ruby]
if packet[3] > 130 && packet[3] <  153 && packet[5] > 913 && packet[5] < 937
  is_tor = true
else
  is_tor = false
end
\end{lstlisting}

Applying this algorithm to a 10\% sample of each of the packet traces yields
the results as seen in table \ref{table:heuristic-results}.

\begin{table}[H]
  \begin{tabular*}{\linewidth}{lr}
    \toprule
    Protocol & Identified as Tor\\
    \midrule
    HTTPS & 0.0000\% \\
    HTTP over Tor & 0.9903\% \\
    HTTPS over Tor & 0.9826\% \\
    \bottomrule
  \end{tabular*}
  \caption{Results}
  \label{table:heuristic-results}
\end{table}
